---
title: "Quezon City Epidemiolgy and Surveillance Unit"
author: 'Covid-19 Report and Analysis'
---

```{r setup,include=FALSE}
knitr::opts_chunk$set(fig.align = "center", echo = FALSE)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(lubridate)
library(ggthemes)
library(DT)
library(readxl)
source("New priority Script.R")
today <- format(Sys.time(),"%m/%d/%Y %H:%M:%S")
```

## Monitoring of Reported Cases {.tabset}

### Daily Count 

Last refreshed date : `r today`

- Total number of Reported Cases : `r Reported_count`
  - Total number of Endorsed Cases to Field Team: `r Endorsed_count_d`
  - Total Number of Out of City Cases : `r OZ_count_d`
  - Total Number of Already Visited by CESU : `r Visited_count_d`
  - Total Number of Pending : `r Pending_count_d`
    - Confirmed cases : `r C_pending_count_d`
    - Probable cases : `r P_pending_count_d`
    - Suspect cases : `r S_pending_count_d`
  - Total Number of Unable to contact : `r Unable_to_contact_d`
    - Count of Wrong number : `r Wrong_number_d`
    - Total Number of Cannot be reached : `r Cannot_be_reach_d`
    - Total Number of Dropped call : `r Droppedcall_count_d`
    - Total Number of Wrong person : `r Wrong_person_d`
    - Total Number of Not answering the phone : `r NATPhone_d`
  - Total number of confirmed cases with no number indicated: `r No_number_d`
  
Below is the cumulative count of reported cases today distributed by patient classification 
```{r}
NPC_classification <- NPC %>%
  filter(`Report date` == Sys.Date()) %>% 
  group_by(`Patient classification`) %>% 
  count(name = "Count")

DT::datatable(NPC_classification , rownames = FALSE,
          filter = list(position = 'bottom', clear = FALSE, plain = TRUE),
          options = list(autoWitdh =TRUE,
                         columnDefs = list(list(className = 'dt-center',
                                                targets = "_all"))))
```
  
### Cumulative Count

- Total number of Reported Cases : `r Reported_count_cumulative`
  -  Number of confirmed Cases 'Endorsed  to Field Team' : `r Endorsed_count_cum`
  -  Number of 'Out of City' confirmed Cases : `r OZ_count_cum`
  -  Number of confirmed cases 'Already Visited by CESU' : `r Visited_count_cum`
  -  Number of Pending : `r Pending_count_cum`
    - Confirmed cases : `r C_pending_count_cum`
    - Probable cases : `r P_pending_count_cum`
    - Suspect cases : `r S_pending_count_cum`
  - Total Number of Unable to contact : `r Unable_to_contact_cum`
    - Count of Wrong number : `r Wrong_number_cum`
    - Total Number of Cannot be reached : `r Cannot_be_reach_cum`
    - Total Number of Dropped call : `r Droppedcall_count_cum`
    - Total Number of Wrong person : `r Wrong_person_cum`
    - Total Number of Not answering the phone : `r NATPhone_cum`
  - Total number of confirmed cases with no number indicated: `r No_number_cum`
  
Below is the cumulative count of cases distributed by patient classification since January 17, 2021
```{r}
NPC_classification <- NPC %>%
  group_by(`Patient classification`) %>% 
  count(name = "Count")

DT::datatable(NPC_classification , rownames = FALSE,
          filter = list(position = 'bottom', clear = FALSE, plain = TRUE),
          options = list(autoWitdh =TRUE,
                         columnDefs = list(list(className = 'dt-center',
                                                targets = "_all"))))
```
  

## Output of Phone Contact Tracers {.tabset}

### Confirmed cases per barangay

Cumulative number of Covid-19 cases per Barangay
```{r, echo = FALSE}
NPC_bgry_table <- NPC %>% 
  group_by(Barangay) %>% 
  summarise(Count = sum(n()), .groups = "drop") %>% 
  arrange(desc(Count))

DT::datatable(NPC_bgry_table, rownames = FALSE,
          filter = list(position = 'bottom', clear = FALSE, plain = TRUE),
          options = list(autoWitdh =TRUE,
                         columnDefs = list(list(className = 'dt-center',
                                                targets = "_all"))))
```

### Type of exposure

Top 10 Covid-19 Cases exposure collected by phone tracers for past 14 days

```{r}
NPC_exposure <- NPC %>%
  filter(`Report date` >= Sys.Date() - 14, `Type of exposure` != "UTC",
         `Type of exposure` != "match not found",
         !str_detect(Remarks, "UNABLE")) %>%
  select(`Type of exposure`) %>%
  group_by(`Type of exposure`) %>%
  summarise('Count' = sum(n()), .groups = "drop") %>% 
  arrange(desc(`Count`))

DT::datatable(NPC_exposure, rownames = FALSE,
          filter = list(position = 'bottom', clear = FALSE, plain = TRUE),
          colnames = c("Exposure type","Count"),
          options = list(autoWitdh =TRUE, columnDefs = list(list(className = 'dt-center',
                                                targets = "_all"))))
```
```{r}
rm(list = ls())
```