---
title: "Data Reconciliation Report"
author: "DOH linelist vs CESU linelist summary"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(lubridate)
library(ggthemes)
library(DT)
library(readxl)
source("Linelist script.R")

```


```{r fig.width=10, echo=FALSE}
reported_cases_table <- ll %>% 
  group_by(report_date) %>% 
  summarise(Cases = sum(n()), .groups = "drop") 

average_count = round(mean(reported_cases_table$Cases),0)

ggplot(reported_cases_table, aes(x = report_date, y = Cases)) +
  geom_col(fill = "blue") +
  geom_text(aes(label = Cases), vjust = -0.5) +
  scale_x_date(date_breaks = "1 day", date_labels = "%Y-%m-%d") +
  labs(title = paste0("NUMBER OF DOH REPORTED CASES PER DAY ( Average Daily Cases = ", average_count," )"),
       x = "Report date",
       y = "Count of Cases") +
  theme_classic() + theme(axis.text.x = element_text(angle = 45, hjust = 1),
                          plot.title = element_text(hjust = 0.5))

beginning_date <- min(ll$report_date)
up_to_date <- max(ll$report_date)
```

## REPORT DETAILS

DATE OF REPORT : `r beginning_date` - `r up_to_date`


- TOTAL NUMBER OF REPORTED CASE: `r total_reported_cases`
  - Total number of cases found on CESU linelist: `r mdb_found_count`
    - Number of verified cases: `r v_count`
    - Number of unverified cases: `r to_input_mdb`
      - Tagged as Investigated by District NPC encoders:
        - Number of cases already field traced: `r investigated_1stbd_ft`
        - Number of cases endorsed to other city: `r investigated_1stbd_ETOC`
        - Number of cases endorsed to other district: `r investigated_1stbd_ETOD`
        - Number of cases tagged as non-resident: `r investigated_1stbd_NR`
        - Number of cases unable to locate: `r investigated_1stbd_UTL`
        - Number of cases without remark: `r investigated_1stbd_No_remark`
        - Number of duplicate cases: `r investigated_1stbd_DC`
      - Count of cases still in under field investigation : `r notinvestigated_1st`
      
      
- Balance : `r balance`


  - Total number of cases found on New Priority Case repository: `r found_on_npc`
    - Count of cases tagged as out of city area : `r OZ_count_npc`
    - Other tagging: 
      -   suspect pending: `r suspect_pending_npc `
      -   Already in CESU line list: `r AIMDB_npc`
      -   Unable to contact: `r UTC_npc`
      - Count of cases endorsed to field team: `r RFHH_npc`
        - Tagged as Investigated by District NPC encoders:
          - Number of cases already field traced: `r investigated_2ndbd_ft`
          - Number of cases endorsed to other city: `r investigated_2ndbd_ETOC`
          - Number of cases endorsed to other district: `r investigated_2ndbd_ETOD`
          - Number of cases tagged as non-resident: `r investigated_2nd_NR`
          - Number of cases unable to locate: `r investigated_2ndbd_UTL`
          - Number of cases without remark: `r investigated_2ndbd_No_remark`
          - Number of duplicate cases: `r investigated_2ndbd_DC`
        - Count of on-going field investigation : `r notinvestigated_2nd`
      
      
- Discrepancy : `r discrepancy`
      
  
      


    
    


